TRTF and TTM Pseudocode

### 2025-08-28 docs/trtf_ttm_pseudocode.Rmd
Kernel-Smoother vollständig entfernt
.

Let $\pi(x)$ denote the target log density and $\eta(z)$ the base log density. The triangular transport map $S: \mathbb{R}^K \to \mathbb{R}^K$ has components $S_k(x_1,\ldots,x_k)$ for $k=1,\ldots,K$. Here $N$ is the number of observations and $K$ the dimension of $x$. The change of variables states, in words, that the log density of $x$ under $\pi$ equals the log density of $S(x)$ under $\eta$ plus the log determinant of the Jacobian, which reduces to a sum of log partial derivatives because $S$ is triangular. The pipeline main() -> TRUE/TRTF/KS/TTM marginal governs all experiments. Model artifacts are TRTF and the Marginal Map (diagonal). All log densities are measured in nats, and sums over dimensions yield the joint log density.

>>>>

Let $\pi(x)$ denote the target log density and $\eta(z)$ the base log density. The triangular transport map $S: \mathbb{R}^K \to \mathbb{R}^K$ has components $S_k(x_1,\ldots,x_k)$ for $k=1,\ldots,K$. Here $N$ is the number of observations and $K$ the dimension of $x$. The change of variables states, in words, that the log density of $x$ under $\pi$ equals the log density of $S(x)$ under $\eta$ plus the log determinant of the Jacobian, which reduces to a sum of log partial derivatives because $S$ is triangular. The pipeline main() -> TRUE/TRTF/TTM marginal governs all experiments. Model artifacts are TRTF and the Marginal Map (diagonal). All log densities are measured in nats, and sums over dimensions yield the joint log density. For the cross‑term map (Eq. 22), training uses only train/test splits (no validation/CV); L2 ridge weights and quadrature nodes are configured via R options (`mde.ctm.*`) or environment variables (`MDE_CTM_*`).
